France has enjoyed a long and storied history as a world leader in culture, food,
literature, film, and revolutions. Over its history, the average life expectancy of people in France
has changed notably. The time series object described below contains the annual average life
expectancy in France (measured in years lived), measured during the years 1816 to 2019. The
data is in the file FLE.txt. \\

\noindent Analyze the data in the time series and write a report addressing the following:

\begin{enumerate}[label=(\alph*)]
    \item What trend model(s) best capture the trends in French life expectancy over time?
    \item Are there any noticeable patterns, or observations apparent in the series? Can you tell form
your plot what could be the causes of your observations?
    \item Regardless of what you observe, suppose you apply some transformation to the data, how
does the new data looks like? Any changes in trend?
    \item For the various models you tried, assess the fit of the models using any tools at your disposal. Perform any necessary test to make sure sure your model is appropriate. Write down the equation of your final model. Are any transformations of the data necessary? Perform all diagnostics tests.
\end{enumerate}

\noindent Now conclude with brief summary: How the life expectancy changes over time, both long-term
over the observed period of years, and in terms of patterns of year-to-year variation. Add any
necessary graphs, tests and/or confidence interval etc...

\subsection{R Code}
\subsection{Results}